Title

### 2012-02-24 inc/magnetic_lenses/maglens.tex
Continue magnetic lenses. added schematic figure

While in principle one could design a magnetic lens using equations \ref{eq:lens_eq_of_motion} and \ref{eq:field_of_loop}, the process wouldn't be very practical or instructive.
Further --- as suggested by the use of the $H$ field in \ref{eq:field_of_loop} --- better performance of the lens can be achieved by concentrating the field using materials with high magnetic permeablility; this component is called a ``pole piece''.

>>>>

While in principle one could design a magnetic lens using \ref{eq:lens_eq_of_motion} and \ref{eq:field_of_loop}, the process wouldn't be very practical or instructive.
Further --- as suggested by the use of the $H$ field in \ref{eq:field_of_loop} --- better performance of the lens can be achieved by concentrating the field using materials with high magnetic permeablility.
These materials, called ``magnetic shielding'' since it captures the magnetic field lines, can direct the field lines to a small gap, known as the ``pole-piece gap''.
The field lines exit the shielding in the gap and it is this field that acts as the lens.
This gap can be much smaller than the total width of the coil turns, and yet contain in a field commensurate with the full coil.

\begin{figure}
\centering
\begin{tikzpicture}
  \foreach \n in {0,0.1,...,0.6}{
    \draw [red] (0.75,-0.5) ellipse [x radius=\n,y radius=0.6];
  }
  \foreach \n in {0,0.1,...,0.6}{
    \draw [red] (-0.75,-0.5) ellipse [x radius=\n,y radius=0.6];
  }
  \draw [fill=blue!50] 
    (-0.5,0)
    -- ++(0,2)
    -- ++(-2,0)
    -- ++(0,-5)
      node [pos=0.5,left,align=right] {Magnetic\\Shielding}
    -- ++(2,0)
    -- ++(0,2)
      coordinate [pos=0] (D left)
    -- ++(-0.5,0)
      coordinate [pos=0.5] (S top)
    -- ++(0,-1.5)
    -- ++(-1,0)
    -- ++(0,4)
    -- ++(1,0)
    -- ++(0,-1.5)
    -- ++(0.5,0)
      coordinate [pos=0.5] (S bottom)
    -- cycle
  ;
  \draw [fill=blue!50] 
    (0.5,0)
    -- ++(0,2)
    -- ++(2,0)
    -- ++(0,-5)
    -- ++(-2,0)
    -- ++(0,2)
      coordinate [pos=0] (D right)
    -- ++(0.5,0)
    -- ++(0,-1.5)
    -- ++(1,0)
    -- ++(0,4)
    -- ++(-1,0)
    -- ++(0,-1.5)
    -- cycle
  ;
  \draw [thick, dashed]
    (0,3)
    -- (0,-3)
  ;
  \draw [very thick,<->] 
    (S top) 
    -- (S bottom)
      node [pos=0.5,fill=white] {$S$}
  ;
  \draw [very thick,<->] 
    (D left) 
    -- (D right)
      node [below,pos=0.5,align=center] {$D$\\$(=2R)$}
  ;
  \node [rotate=90] at (-1.6,-0.5) {Windings};
  \node [red,rotate=90] at (1.6,-0.5) {Field Lines};
\end{tikzpicture}
\end{figure}

El-Kareh and El-Kareh \cite{el-kareh_electron_1970} provides an analysis of symmetric lenses with magnetic shielding and a pole-piece in chapter 8, with the most useful information being in section 8.7.
